Detecting Facial Expressions in Professional Tennis Matches

### 2017-03-01 Report06-12.Rmd
Data cleaning, updated files

#Factor Names 
ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))
ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 0:2, labels = c("Direct sunlight", "Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))

>>>>

#Factor Names 
ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))
